---
title: "github.com/openpharma"
output: 
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: minty
    orientation: rows
    social: menu
    source_code: embed
    navbar:
      - { title: "Github", href: "https://github.com/openpharma/", align: right, icon: github}
---

```{r, include=FALSE}
library(flexdashboard)
library(ggplot2)

library(dplyr)
library(lubridate)
library(glue)
library(tidyr)
library(fontawesome) # devtools::install_github("rstudio/fontawesome")



thematic::thematic_rmd(
  font = "auto",
  # To get the dark bg on the geom_raster()
  sequential = thematic::sequential_gradient(fg_low = FALSE, fg_weight = 0, bg_weight = 1)
)
theme_set(theme_bw(base_size = 20))
```

```{r getdata}
library(pins)
  pins::board_register_github(
    repo = "openpharma/openpharma_log", branch = "main"
    )
  
  commits <- pin_get("all-commits", board = "github")
  contributors <- pin_get("all-contributors", board = "github")
  repos <- pin_get("all-repos", board = "github", cache = FALSE)
  issues <- pin_get("all-issues", board = "github", cache = FALSE)
  tags <- pin_get("all-tags", board = "github", cache = FALSE)
```

```{r prepdata}
repos <- repos %>%
  mutate(
    language = case_when(
      repo %in% tags$r ~ as.character(fa("r-project", fill = "steelblue")),
      repo %in% tags$python ~ as.character(fa("python", fill = "goldenrod"))
    )
  )
```

Organization
===================================== 

Value Boxes {data-width=200}
-------------------------------------

### Primary

```{r}
valueBox(n_distinct(repos$repo), caption = "Total repos", icon = "fa-github")
```

### Commits

```{r}
valueBox(nrow(commits), caption = "Commits", color = "success", icon = "fa-code-branch")
```

### People

```{r}
valueBox(
  n_distinct(contributors$author), 
  caption = "People", color = "success", icon = "fa-users")
```

### Issues

```{r}
valueBox(
  issues %>% filter(state == "open") %>% nrow(), 
  caption = "Open Issues", color = "warning", icon = "fa-question")
```

### Companies

```{r}
valueBox(
  glue("~{n_distinct(contributors$company)}"), 
  caption = "Unique employers", color = "success", icon = "fa-building")
```

Value Boxes {data-width=200}
-------------------------------------


### 

```{r}
lookback <- 30*3
lookback_char <- "3 months"

valueBox(
  commits %>%
    filter(date > Sys.Date() - lookback) %>%
    pull(full_name) %>% n_distinct(),
  caption = glue("Repos active | Last {lookback_char}"), 
  color = "info", icon = "fa-chart-line"
  )
```

### 

```{r}
valueBox(
  commits %>%
    filter(date > Sys.Date() - lookback) %>%
    nrow(),
  caption = glue("Commits | Last {lookback_char}"),
  color = "info", icon = "glyphicon-time")
```

### 

```{r}
valueBox(
  commits %>%
    filter(date > Sys.Date() - lookback) %>%
    pull(author) %>% n_distinct(),
  caption = glue("People active | Last {lookback_char}"), 
  color = "info", icon = "glyphicon-time")
```

### 

```{r}
valueBox(
  length(tags$python), 
  caption = "Python libraries", color = "info",
  icon = "fab fa-python"
)
```

### 

```{r}
valueBox(
  length(tags$r), 
  caption = "R packages", color = "info",
  icon = "fab fa-r-project"
)
```

    
Tables {.tabset}
-------------------------------------

### Repositories
    
```{r}
hlp_repo_details <- function(x){
  DT::datatable(
      x %>%
          mutate(
            `Last updated` = as.Date(updated_at),
            Repo = glue(
              '<a href="https://github.com/{full_name}">{full_name}</a>'
              )
            ) %>%
          arrange(desc(`Last updated`)) %>%
          select(
              Repo,
              Description = description,
              `Type` = language,
              `Last updated`
          ), 
      rownames = FALSE,
      escape = FALSE,
      fillContainer = TRUE)  
}

hlp_repo_details(repos)
```

### People
    
```{r}
DT::datatable(
  contributors %>%
    left_join(
      commits %>%
        group_by(author) %>%
        summarise(
          contributed_to = n_distinct(full_name),
          commits = n()
        ),
      by = "author"
    ) %>%
    mutate(
      last_active = Sys.Date() - last_active,
      contributor = as.character(glue(
        '<img src="{avatar}" alt="" height="30" width = "30"> {name} (<a href="https://github.com/{author}">{author}</a>)'
        )),
      Blog = case_when(
        blog == "" ~ "",
        TRUE ~ as.character(glue('<a href="{blog}">link</a>'))
        ),
      Name = glue("{name} ({author})")
      ) %>%
    arrange(last_active, desc(contributed_to), desc(commits)) %>%
    select(
      `Name (GH handle)` = contributor,
      Repos = contributed_to,
      `Commits` = commits,
      `Days since active` = last_active,
      Company = company,
      Location = location,
      Blog
      ) , 
    escape = FALSE,
    rownames = FALSE,
    fillContainer = TRUE)
```
### Health
    
```{r}
# kaplan mier estimate?


repos %>%
  mutate(
    days_since_update = as.numeric(Sys.Date() - as.Date(updated_at))
  ) %>%
  select(full_name, days_since_update) %>%
  left_join(
    # time current open
    issues %>%
      group_by(full_name) %>%
      filter(state == "open") %>%
      summarise(
        open_issues = n(),
        median_age_open_issue = median(days_open),
        median_inactivity_open_issue = median(days_no_activity)
      ),
    by = "full_name"
  ) %>%
  left_join(
    # time to close
    issues %>%
      group_by(full_name) %>%
      filter(state == "closed") %>%
      summarise(
        closed_issues = n(),
        median_timeto_close = median(days_open)
      )  ,
    by = "full_name"  
  ) %>%
  left_join(
    # increase in commits?
    commits %>%
      group_by(full_name) %>%
      mutate(
        date_numeric = as.numeric(date),
        midpoint = quantile(date_numeric, 0.5),
        firsthalf = ifelse(date_numeric >= midpoint,FALSE,TRUE)
      ) %>%
      summarise(
        commits = n(),
        secondhalf = sum(ifelse(!firsthalf,1,0)),
        firsthalf = sum(ifelse(firsthalf,1,0))
      ) %>%
      mutate(
        abs = secondhalf - firsthalf
      ) %>%
      select(
        full_name, abs_commits = abs,commits
      )   ,
    by = "full_name" 
  ) %>%
  left_join(
    # increase in people?
    commits %>%
      group_by(full_name) %>%
      summarise(
        authors_ever = n_distinct(author)
      ),
    by = "full_name"
  ) %>%
  left_join(
    # increase in people?
    commits %>%
      group_by(full_name) %>%
      mutate(
        date_numeric = as.numeric(date),
        midpoint = quantile(date_numeric, 0.5),
        timing = ifelse(date_numeric >= midpoint,"firsthalf","secondhalf")
      ) %>%
      group_by(full_name,timing) %>%
      summarise(
        active_people = n_distinct(author)
      ) %>% ungroup %>%
      pivot_wider(
        names_from = timing, values_from = active_people, values_fill = 0
      ) %>%
      mutate(
        ratio = secondhalf/firsthalf,
        abs_people = secondhalf-firsthalf,
        percentage_people = round(100*ratio),
        # if one commit set to 0
        percentage_people = ifelse(percentage_people == Inf,0,percentage_people)
      ) %>%
      select(full_name,abs_people),
    by = "full_name"
  ) %>%
  # Score
  mutate(
    score = ifelse(days_since_update < 30*6,1,0),
    score = case_when(
      is.na(sum(open_issues,closed_issues, na.rm = TRUE)) ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      commits < 25 ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      authors_ever < 5 ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      is.na(median_age_open_issue) ~ score,
      median_age_open_issue > 30*6 ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      is.na(median_inactivity_open_issue) ~ score,
      median_inactivity_open_issue > 30*3 ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      is.na(open_issues) | is.na(closed_issues) ~ score,
      open_issues > closed_issues ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      is.na(abs_commits)  ~ score,
      abs_commits < 0 ~ score,
      TRUE ~ score + 1
    ),
    score = case_when(
      is.na(abs_people)  ~ score,
      abs_people < 0 ~ score,
      TRUE ~ score + 1
    ),
    Health = round(100*score/max(score)),
    
    Repo = glue(
      '<a href="https://github.com/{full_name}">{full_name}</a>'
      )
  ) %>%
  # tidy title
  select(
    Repo,
    Health,
    Commits = commits,
    Contributors = authors_ever,
    `Days repo inactive` = days_since_update,
    `Median days open for current issues` = median_age_open_issue,
    `Median days without comments on open issues` = median_inactivity_open_issue,
    `Median days to close issue` = median_timeto_close,
    `Change in frequency of commits` = abs_commits,
    `Change in active contributors` = abs_people
  ) %>%
  arrange(
    desc(Health)
  ) %>%
  # table it
  DT::datatable(
    escape = FALSE,
    rownames = FALSE,
    fillContainer = TRUE
    )
```

> For details  on the metrics, please see XXXXXX

Filing tools {data-navmenu="Categories"}
=====================================  

blah 
-------------------------------------
   
### 

```{r}
hlp_repo_details(
  repos %>% filter(repo %in% tags$filing)
)
```  

Tables, listings, graphs {data-navmenu="Categories"}
=====================================  

blah 
-------------------------------------

### 

```{r}
hlp_repo_details(
  repos %>% filter(repo %in% tags$tlg)
)
```  

Manifesto
=====================================     
   
Column 
-------------------------------------

### Manifesto

The objective of the Github [organisation github.com/openpharm](https://github.com/openpharma) (openpharma) is to provide a neutral home for open source software that is not tied to one company or institution. This Github organization is managed under the following principals:

Hosting repositories in a neutral space:

* openpharma allows repositories housed within it to set their own governance model
* openpharma is open to any project related to the Pharma industry
* openpharma makes no assumptions on what packages are part of an ‘ideal’ workflow
* a preference is always placed on opensource from day 1, but openpharma will also host packages in private repos on request
* [at launch, Roche has admin status for the organization] openpharma will work towards a governance model that is inclusive and builds trust in those contributing to packages (e.g. use a more formalized consortia like the pharmaverse to provide governance of the Github organization)
* openpharma is open to collaborating with relevant organizations like PHUSE, R Consortium, PSI and the pharmaverse – but  openpharma will remain an open host to share projects and provide a platform for repositories looking for a neutral host. 
* openpharma will not hold any IP or copyright of associated projects, it will not be a platform for discussion or host initiatives, and it will not release opinions or standards on which repositories form part of an ideal workflow.

Promoting collaboration on projects:

* openpharma will aim to build an inclusive list of collaborative projects hosted on github.com that goes beyond those physically hosted in github.com/openpharma.
* openpharma will surface these projects to encourage collaboration (e.g. provide a front end like https://insights.lfx.linuxfoundation.org/projects). As a starter, a proof of concept
has been made (this site)


### Links

- R/Pharma conference: [rinpharma.com](https://rinpharma.com/)
- R Consortium: [r-consortium.org](https://www.r-consortium.org/)
- Get your R project funded!: [ISC](https://www.r-consortium.org/projects/call-for-proposals)
