---
title: "github.com/openpharma"
output: 
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      bootswatch: minty
    orientation: rows
    social: menu
    source_code: https://github.com/openpharma/openpharma.github.io
    navbar:
      - { title: "Github", href: "https://github.com/openpharma/", align: right, icon: github}
---

```{r, include=FALSE}
library(flexdashboard)
library(ggplot2)

library(dplyr)
library(lubridate)
library(glue)
library(tidyr)
library(fontawesome) # devtools::install_github("rstudio/fontawesome")
library(plotly)

library(purrr)
library(dm)
library(DiagrammeR)



thematic::thematic_rmd(
  font = "auto",
  # To get the dark bg on the geom_raster()
  sequential = thematic::sequential_gradient(fg_low = FALSE, fg_weight = 0, bg_weight = 1)
)
theme_set(theme_bw(base_size = 20))
```

```{r getdata}
library(readr)
  commits <- read_rds("scratch/gh_commits.rds")
  people <- read_rds("scratch/people.rds")
  repos <- read_rds("scratch/repos.rds")
  help <- read_rds("scratch/help.rds")
```


Organization
===================================== 

Value Boxes {data-width=200}
-------------------------------------

### Primary

```{r}
valueBox(n_distinct(repos$repo), caption = "Total repos", icon = "fa-github")
```

### Commits

```{r}
valueBox(nrow(commits), caption = "Commits", color = "success", icon = "fa-code-branch")
```

### People

```{r}
valueBox(
  n_distinct(people$author), 
  caption = "People", color = "success", icon = "fa-users")
```

### Intro issues

```{r}
valueBox(
  help  %>% nrow(), 
  caption = "Open issues needing help", color = "warning", icon = "fa-question")
```

### Companies

```{r}
valueBox(
  n_distinct(people$company), 
  caption = "Unique employers", color = "success", icon = "fa-building")
```

Value Boxes {data-width=200}
-------------------------------------


### 

```{r}
lookback <- 30*3
lookback_char <- "3 months"

valueBox(
  commits %>%
    filter(date > Sys.Date() - lookback) %>%
    pull(full_name) %>% n_distinct(),
  caption = glue("Repos active | Last {lookback_char}"), 
  color = "info", icon = "fa-chart-line"
  )
```

### 

```{r}
valueBox(
  commits %>%
    filter(date > Sys.Date() - lookback) %>%
    nrow(),
  caption = glue("Commits | Last {lookback_char}"),
  color = "info", icon = "glyphicon-time")
```

### 

```{r}
valueBox(
  commits %>%
    filter(date > Sys.Date() - lookback) %>%
    pull(author) %>% n_distinct(),
  caption = glue("People active | Last {lookback_char}"), 
  color = "info", icon = "glyphicon-time")
```

### 

```{r}
valueBox(
  repos %>% filter(lang == "python") %>% nrow(), 
  caption = "Python libraries", color = "info",
  icon = "fab fa-python"
)
```

### 

```{r}
valueBox(
  repos %>% filter(lang == "r") %>% nrow(), 
  caption = "R packages", color = "info",
  icon = "fab fa-r-project"
)
```

    
Tables {.tabset}
-------------------------------------

### Repositories
    
```{r}
hlp_repo_details <- function(x){
  DT::datatable(
      x %>%
          mutate(
            `Last updated` = as.Date(gh_updated),
            ) %>%
          arrange(desc(`Last updated`)) %>%
          select(
              Repo = pretty_repo,
              Description = imputed_description,
              `Type` = lang,
              `Last updated`,
              `Contributor overlap` = similar
          ), 
      rownames = FALSE,
      escape = FALSE,
      fillContainer = TRUE)  
}

hlp_repo_details(repos)
```

### People
    
```{r, echo = FALSE}
DT::datatable(
  people %>%
    mutate(my = format(last_active, "%Y-%m")) %>% 
    group_by(my) %>% mutate(month_commits = sum(commits)) %>% ungroup %>%
    mutate(
      last_active = Sys.Date() - last_active,
      contributor = as.character(glue(
        '<img src="{avatar}" alt="" height="30" width = "30"> {name} (<a href="https://github.com/{author}">{author}</a>)'
        )),
      Blog = case_when(
        blog == "" ~ "",
        TRUE ~ as.character(glue('<a href="{blog}">link</a>'))
        ),
      Name = glue("{name} ({author})")
      ) %>%
    arrange(desc(my),desc(month_commits), desc(contributed_to), desc(commits)) %>%
    select(
      `Name (GH handle)` = contributor,
      Repos = contributed_to,
      `Repo list` = repo_list,
      `Commits` = commits,
      `Days since active` = last_active,
      Company = company,
      Location = location,
      Blog
      ) , 
    escape = FALSE,
    rownames = FALSE,
    fillContainer = TRUE)
```

### Health
    
```{r}
# kaplan mier estimate?


repos %>%
  # tidy title
  select(
    Repo = pretty_repo,
    Health,
    Commits,
    Contributors,
    `Days repo inactive`,
    `Median days open for current issues`,
    `Median days without comments on open issues`,
    `Median days to close issue`,
    `Change in frequency of commits`,
    `Change in active contributors`
  ) %>%
  arrange(
    desc(Health)
  ) %>%
  # table it
  DT::datatable(
    escape = FALSE,
    rownames = FALSE,
    fillContainer = TRUE
    )
```

### Growth

```{r}
### People activity over time
plot <- commits %>%
  mutate(
    month = format(date, "%m"), 
    year = format(date, "%Y"),
    year_mon = as.Date(glue("{year}-{month}-01"))
    ) %>%
  group_by(year_mon) %>%
  summarise(
    Repos = n_distinct(full_name),
    People = n_distinct(author)
  ) %>%
  filter(year_mon >= as.Date("2020-01-01")) %>%
  pivot_longer(
    !year_mon,
    names_to = "Active by month",
    values_to = "Value"
  ) %>%
  # remove last 
  group_by(`Active by month`) %>%
  arrange(year_mon) %>%
  slice(1:(n() - 1)) %>%
  ggplot(
    aes(
      year_mon, 
      Value, 
      group = `Active by month`,
      colour = `Active by month`
    )
  ) +
  geom_line() +
  geom_point() +
  labs(
    title = "Active repos and people defined by monthly commit activity",
    x = "Monthly",
    y = "Active"
  ) + theme(legend.title = element_blank())

ggplotly(plot)
```

### Growth - with denominator

```{r}
range <- commits %>%
  mutate(
    month = format(date, "%m"), 
    year = format(date, "%Y"),
    year_mon = as.Date(glue("{year}-{month}-01"))
  ) %>%
  summarise(
    min = min(year_mon), max = max(year_mon)
  )

### People activity over time
plot <- commits %>%
  mutate(
    month = format(date, "%m"), 
    year = format(date, "%Y"),
    year_mon = as.Date(glue("{year}-{month}-01"))
    ) %>%
  group_by(year_mon) %>%
  summarise(
    Repos = n_distinct(full_name),
    People = n_distinct(author)
  ) %>%
  left_join(
    tibble(
  year_mon = seq.Date(range$min, range$max, by=1)
  ) %>%
  left_join(
    commits %>%
      mutate(
        month = format(date, "%m"), 
        year = format(date, "%Y"),
        year_mon = as.Date(glue("{year}-{month}-01"))
      ) %>%
      group_by(full_name) %>% 
      arrange(year_mon) %>% slice(1) %>% 
      # check one per date!
      group_by(year_mon) %>% summarise(total = n()),
    by = "year_mon"
  ) %>%
  mutate(
    total = case_when(
      is.na(total) ~ as.integer(0),
      TRUE ~ total
    ),
    tracked_repos = cumsum(total)
  ) %>%
  select(year_mon, `Repo's tracked` = tracked_repos),
    by = "year_mon"
  ) %>%
  filter(year_mon >= as.Date("2020-01-01")) %>%
  pivot_longer(
    !year_mon,
    names_to = "Active by month",
    values_to = "Value"
  ) %>%
  # remove last 
  group_by(`Active by month`) %>%
  arrange(year_mon) %>%
  slice(1:(n() - 1)) %>%
  ggplot(
    aes(
      year_mon, 
      Value, 
      group = `Active by month`,
      colour = `Active by month`
    )
  ) +
  geom_line() +
  geom_point() +
  labs(
    title = "Active repos and people defined by monthly commit activity",
    x = "Monthly",
    y = "Active"
  ) + theme(legend.title = element_blank())

ggplotly(plot)
```


Manifesto
=====================================     
   
Column 
-------------------------------------

### Manifesto

The objective of the Github [organisation github.com/openpharm](https://github.com/openpharma) (openpharma) is to provide a neutral home for open source software that is not tied to one company or institution. This Github organization is managed under the following principals:

Hosting repositories in a neutral space:

* openpharma allows repositories housed within it to set their own governance model
* openpharma is open to any project related to the Pharma industry
* openpharma makes no assumptions on what packages are part of an ‘ideal’ workflow
* a preference is always placed on opensource from day 1, but openpharma will also host packages in private repos on request
* [at launch, Roche has admin status for the organization] openpharma will work towards a governance model that is inclusive and builds trust in those contributing to packages (e.g. use a more formalized consortia like the pharmaverse to provide governance of the Github organization)
* openpharma is open to collaborating with relevant organizations like PHUSE, R Consortium, PSI and the pharmaverse – but  openpharma will remain an open host to share projects and provide a platform for repositories looking for a neutral host. 
* openpharma will not hold any IP or copyright of associated projects, it will not be a platform for discussion or host initiatives, and it will not release opinions or standards on which repositories form part of an ideal workflow.

Promoting collaboration on projects:

* openpharma will aim to build an inclusive list of collaborative projects hosted on github.com that goes beyond those physically hosted in github.com/openpharma.
* openpharma will surface these projects to encourage collaboration (e.g. provide a front end like https://insights.lfx.linuxfoundation.org/projects). As a starter, a proof of concept
has been made (this site)


### Links

- R/Pharma conference: [rinpharma.com](https://rinpharma.com/)
- R Consortium: [r-consortium.org](https://www.r-consortium.org/)
- Get your R project funded!: [ISC](https://www.r-consortium.org/projects/call-for-proposals)

Data
=====================================    
   
Row 
-------------------------------------

### Details on the data pull

The data for this site builds daily. You can access the latest metadata via the 
links on this page. See the Snakefile for an example of the build
process

The code that generates this data is in the repo
[openpharma/openpharma.github.io](https://github.com/openpharma/openpharma.github.io)

<svg width="423pt" height="248pt"
 viewBox="0.00 0.00 423.26 247.62" xmlns="http://www.w3.org/2000/svg" xmlns:xlink="http://www.w3.org/1999/xlink">
<g id="graph0" class="graph" transform="scale(1 1) rotate(0) translate(4 243.619)">
<title>snakemake_dag</title>
<polygon fill="#ffffff" stroke="transparent" points="-4,4 -4,-243.619 419.259,-243.619 419.259,4 -4,4"/>
<!-- 0 -->
<g id="node1" class="node">
<title>0</title>
<path fill="none" stroke="#59d856" stroke-width="2" d="M83.519,-137.8095C83.519,-137.8095 12.16,-137.8095 12.16,-137.8095 6.16,-137.8095 .16,-131.8095 .16,-125.8095 .16,-125.8095 .16,-113.8095 .16,-113.8095 .16,-107.8095 6.16,-101.8095 12.16,-101.8095 12.16,-101.8095 83.519,-101.8095 83.519,-101.8095 89.519,-101.8095 95.519,-107.8095 95.519,-113.8095 95.519,-113.8095 95.519,-125.8095 95.519,-125.8095 95.519,-131.8095 89.519,-137.8095 83.519,-137.8095"/>
<text text-anchor="middle" x="47.8395" y="-116.8095" font-family="sans" font-size="10.00" fill="#000000">Generate dashboard</text>
</g>
<!-- 1 -->
<g id="node2" class="node">
<title>1</title>
<path fill="none" stroke="#d8ac56" stroke-width="2" d="M186.4325,-137.8095C186.4325,-137.8095 148.9255,-137.8095 148.9255,-137.8095 142.9255,-137.8095 136.9255,-131.8095 136.9255,-125.8095 136.9255,-125.8095 136.9255,-113.8095 136.9255,-113.8095 136.9255,-107.8095 142.9255,-101.8095 148.9255,-101.8095 148.9255,-101.8095 186.4325,-101.8095 186.4325,-101.8095 192.4325,-101.8095 198.4325,-107.8095 198.4325,-113.8095 198.4325,-113.8095 198.4325,-125.8095 198.4325,-125.8095 198.4325,-131.8095 192.4325,-137.8095 186.4325,-137.8095"/>
<text text-anchor="middle" x="167.679" y="-116.8095" font-family="sans" font-size="10.00" fill="#000000">Merge data</text>
</g>
<!-- 1&#45;&gt;0 -->
<g id="edge1" class="edge">
<title>1&#45;&gt;0</title>
<path fill="none" stroke="#c0c0c0" stroke-width="2" d="M136.8174,-119.8095C127.3575,-119.8095 116.6226,-119.8095 105.9636,-119.8095"/>
<polygon fill="#c0c0c0" stroke="#c0c0c0" stroke-width="2" points="105.8115,-116.3096 95.8115,-119.8095 105.8114,-123.3096 105.8115,-116.3096"/>
</g>
<!-- 2 -->
<g id="node3" class="node">
<title>2</title>
<path fill="none" stroke="#afd856" stroke-width="2" d="M403.22,-137.8095C403.22,-137.8095 339.376,-137.8095 339.376,-137.8095 333.376,-137.8095 327.376,-131.8095 327.376,-125.8095 327.376,-125.8095 327.376,-113.8095 327.376,-113.8095 327.376,-107.8095 333.376,-101.8095 339.376,-101.8095 339.376,-101.8095 403.22,-101.8095 403.22,-101.8095 409.22,-101.8095 415.22,-107.8095 415.22,-113.8095 415.22,-113.8095 415.22,-125.8095 415.22,-125.8095 415.22,-131.8095 409.22,-137.8095 403.22,-137.8095"/>
<text text-anchor="middle" x="371.298" y="-116.8095" font-family="sans" font-size="10.00" fill="#000000">openpharma yaml</text>
</g>
<!-- 2&#45;&gt;1 -->
<g id="edge2" class="edge">
<title>2&#45;&gt;1</title>
<path fill="none" stroke="#c0c0c0" stroke-width="2" d="M327.3664,-119.8095C292.0849,-119.8095 242.9171,-119.8095 208.4898,-119.8095"/>
<polygon fill="#c0c0c0" stroke="#c0c0c0" stroke-width="2" points="208.3105,-116.3096 198.3105,-119.8095 208.3104,-123.3096 208.3105,-116.3096"/>
</g>
<!-- 3 -->
<g id="node4" class="node">
<title>3</title>
<path fill="none" stroke="#56a9d8" stroke-width="2" d="M284.4885,-239.619C284.4885,-239.619 254.4885,-239.619 254.4885,-239.619 248.4885,-239.619 242.4885,-233.619 242.4885,-227.619 242.4885,-227.619 242.4885,-215.619 242.4885,-215.619 242.4885,-209.619 248.4885,-203.619 254.4885,-203.619 254.4885,-203.619 284.4885,-203.619 284.4885,-203.619 290.4885,-203.619 296.4885,-209.619 296.4885,-215.619 296.4885,-215.619 296.4885,-227.619 296.4885,-227.619 296.4885,-233.619 290.4885,-239.619 284.4885,-239.619"/>
<text text-anchor="middle" x="269.4885" y="-218.619" font-family="sans" font-size="10.00" fill="#000000">Github</text>
</g>
<!-- 2&#45;&gt;3 -->
<g id="edge5" class="edge">
<title>2&#45;&gt;3</title>
<path fill="none" stroke="#c0c0c0" stroke-width="2" d="M353.0965,-138.011C336.8816,-154.2259 312.9896,-178.1179 294.8937,-196.2138"/>
<polygon fill="#c0c0c0" stroke="#c0c0c0" stroke-width="2" points="292.1286,-194.0291 287.5324,-203.5751 297.0784,-198.9789 292.1286,-194.0291"/>
</g>
<!-- 4 -->
<g id="node5" class="node">
<title>4</title>
<path fill="none" stroke="#d85656" stroke-width="2" d="M284.4885,-36C284.4885,-36 254.4885,-36 254.4885,-36 248.4885,-36 242.4885,-30 242.4885,-24 242.4885,-24 242.4885,-12 242.4885,-12 242.4885,-6 248.4885,0 254.4885,0 254.4885,0 284.4885,0 284.4885,0 290.4885,0 296.4885,-6 296.4885,-12 296.4885,-12 296.4885,-24 296.4885,-24 296.4885,-30 290.4885,-36 284.4885,-36"/>
<text text-anchor="middle" x="269.4885" y="-15" font-family="sans" font-size="10.00" fill="#000000">Metacran</text>
</g>
<!-- 2&#45;&gt;4 -->
<g id="edge6" class="edge">
<title>2&#45;&gt;4</title>
<path fill="none" stroke="#c0c0c0" stroke-width="2" d="M353.0965,-101.608C336.8816,-85.3931 312.9896,-61.5011 294.8937,-43.4052"/>
<polygon fill="#c0c0c0" stroke="#c0c0c0" stroke-width="2" points="297.0784,-40.6401 287.5324,-36.0439 292.1286,-45.5899 297.0784,-40.6401"/>
</g>
<!-- 3&#45;&gt;1 -->
<g id="edge3" class="edge">
<title>3&#45;&gt;1</title>
<path fill="none" stroke="#c0c0c0" stroke-width="2" d="M251.287,-203.4175C235.0721,-187.2026 211.1801,-163.3106 193.0842,-145.2147"/>
<polygon fill="#c0c0c0" stroke="#c0c0c0" stroke-width="2" points="195.2689,-142.4496 185.7229,-137.8534 190.3191,-147.3994 195.2689,-142.4496"/>
</g>
<!-- 4&#45;&gt;1 -->
<g id="edge4" class="edge">
<title>4&#45;&gt;1</title>
<path fill="none" stroke="#c0c0c0" stroke-width="2" d="M251.287,-36.2015C235.0721,-52.4164 211.1801,-76.3084 193.0842,-94.4043"/>
<polygon fill="#c0c0c0" stroke="#c0c0c0" stroke-width="2" points="190.3191,-92.2196 185.7229,-101.7656 195.2689,-97.1694 190.3191,-92.2196"/>
</g>
</g>
</svg>


These files contains *all* the data up to today, and was pulled ~ `r Sys.time()`.

- Latest repo data ([csv](http://openpharma.s3-website.us-east-2.amazonaws.com/repos.csv), [rds](http://openpharma.s3-website.us-east-2.amazonaws.com/repos.rds))

- Latest people data ([csv](http://openpharma.s3-website.us-east-2.amazonaws.com/people.csv), [rds](http://openpharma.s3-website.us-east-2.amazonaws.com/people.rds))

- Latest who needs help data ([csv](http://openpharma.s3-website.us-east-2.amazonaws.com/help.csv), [rds](http://openpharma.s3-website.us-east-2.amazonaws.com/help.rds))

### Available data



```{r}
dm(repos, people, help) %>%
  dm_add_pk(table = repos, columns = full_name) %>%
  dm_add_pk(table = people, columns = author) %>%
  dm_add_pk(table = help, columns = full_name) %>%
  dm_add_fk(table = repos, columns = full_name, ref_table = help) %>%
  dm_draw(
    view_type = "all", 
    column_types = TRUE, rankdir = "TB")
```

<!-- ### Links to all raw data -->

<!-- ```{r} -->
<!-- readRDS("scratch/s3_contents.rds") %>% knitr::kable() -->
<!-- ``` -->
